Containers and R: the Rockerverse and beyond

### 2019-08-15 manuscript.Rmd
whitespace cleanup
light edits
- mention bioc website and github repository
- don't mention community maintainers by name, to avoid beuracracy of seeking
  approval from them; credit is on github and dockerhub
- italicize _Bioconductor_
- minor word-smithing

Bioconductor is a free, open source and open development project aimed at the analysis and visualization of genetic and genomic data utilizing the R programming language [1]. 
The project currently consists of approximately 1741 R packages and has a semiannual release subsequent to the Comprehensive R Archive Networks release of R [2]. 
Biocondctor release versions are tightly correlated with a version of R. 
Docker images allow availability of current and past versions of R/Bioconductor for convenience and reproducibility.

The Bioconductor docker images are built on top of rocker/r-ver and rocker/rstudio. By utilizing rocker as a base image, the R version and majority of package system dependencies are already included in a Bioconductor base image. 
Bioconductor will install packages based on the selected R version and therefore leverage the rocker/rstudio and rocker/r-ver use of R version tagging. 
Bioconductor selects the desired version of R from rocker, installs BiocManager which will default to the appropriate Bioconductor version, and creates a Bioconductor docker image with a informative tag (R_version_Bioc_version). 
The images are built and distributed to the community through DockerHub [3]. 
All past and current combinations of R and Bioconductor are therefore accessible via a specific docker tag.

The Bioconductor base image contains the minimial system depenedencies and R from rocker, and the BiocManager package for installation of packages configured for the proper version of Bioconductor given the installed R version. 
Bioconductor has several other docker images specific for various areas of research. 
The Bioconductor core image installs the most downloaded Bioconductor packages based on collected statistics. 
The other Bioconductor images are community maintained: Laurent Gatto maintains proteomics images, Steffen Neumann maintains metabolomics images, and the RGLab maintains cytometry images. 
All community maintained images build on top of the Bioconductor base image and therefore indirectly the rocker images [4].

@@

>>>>

_Bioconductor_ is a free, open source and open development project for the analysis and comprehension of genomic data [1].
The project consists of 1741 R software packages, as well as packages containing annotation or experiment data.
_Bioconductor_ has a semiannual release cycle, each release is associated with a particular version of R.
Docker images allow availability of current and past versions of _Bioconductor_ for convenience and reproducibility.

_Bioconductor_ docker images are built on top of rocker/r-ver and rocker/rstudio.
By using rocker as a base image, the R version and most package and system dependencies are included in a _Bioconductor_ base image.
_Bioconductor_ installs packages based on the R version, and therefore leverage the rocker/rstudio and rocker/r-ver use of R version tagging.
_Bioconductor_ selects the desired version of R from rocker, adds the BiocManager CRAN package for installing appropriate versions of _Bioconductor_ packages, and creates a _Bioconductor_ docker image with a informative tag (R\_version\_Bioc\_version).
The images are summarized on the _Bioconductor_ web site [5], maintained in github [6], and available to the community through DockerHub [3].
All past and current combinations of R and _Bioconductor_ are therefore accessible via a specific docker tag.

_Bioconductor_ has several other docker images specific to various areas of research.
The 'core' image installs the most commonly used _Bioconductor_ packages.
Other _Bioconductor_ images for proteomics, metabolomics, and flow cytometry are community maintained.
All community maintained images build on top of the _Bioconductor_ base image and therefore indirectly the rocker images [4].

@@

[5] ?? https://bioconductor.org/help/docker/

[6] ?? https://github.com/Bioconductor/bioc_docker
